All the concepts behind TrueSkill Through Time: the \proglang{Julia}, \proglang{Python} and \proglang{R} packages (Draft)

### 2020-11-22 article.tex
Paper TTT: algunos detalles en el texto

\en{Figure~\ref{fig:generative_model} provides a graphical representation in which skill generate observable results.}

@@

\en{Where $y_{ij}$ is $1$ for winners and $-1$ for losers, and the probability of the observed result given the old estimates can be derived from Figure~\ref{fig:generative_model} (details at section~\ref{sec:exactSolution}).}

@@

>>>>

\en{Figure~\ref{fig:generative_model} provides a graphical representation in which the skill generates observable results.}

@@

\en{where $y_{ij}$ is $1$ for winners and $-1$ for losers, and the probability of the observed result given the old estimates can be derived from Fi.~\ref{fig:generative_model} (more details in section~\ref{sec:exactSolution}).}

@@

\todo[inlin]{Esteban arreglala un poquito para que sea m\'as simple}
